\section{Boids Flocking Algorithm}
I propose to implement Reynolds' original Boids algorithm \cite{reynolds_flocks_1987}, which simulates the flocking behavior of birds through three simple steering behaviors:
%
\begin{itemize}
	\item \textit{Separation}: Avoid crowding nearby flockmates
	\item \textit{Alignment}: Steer towards the average heading of nearby flockmates
	\item \textit{Cohesion}: Steer towards the average position of nearby flockmates
\end{itemize}%
%
Each boid will be modeled as a particle as follows:
\begin{itemize}
	\item Position, velocity and acceleration vector.
	\item Max. Speed and steering force limitations.
	\item A radius for defining which other boids it can "see".
\end{itemize}
For each time step of the simulation the following steps would be computed:
\begin{enumerate}
	\item Compute seperation, alignment and cohesion
	\item Apply weights to each force
	\item Update velocity and position using time integration.
	\item Handling periodic boundary condition.
	\item Render simulation state.
\end{enumerate}
the following parameters could than be systematically change to explore the systems behavior:
\begin{itemize}
	\item Neighborhood radius
	\item Weights of forces
	\item Flock size
\end{itemize}
\subsection{Extensions}
I propose the following possible extension(s) to the basic implementation
\begin{itemize}
	\item \textit{Obstacle Avoidance and other Environmental Factors}
		\begin{itemize}
			\item Add obstacle avoidance steering behavior.
			\item Add wind or similar effects that influences movement.
			\item Create a food source.
		\end{itemize}
	\item \textit{Leadership Dynamics}
		\begin{itemize}
			\item Implement a "follow the leader" steering behavior.
			\item Different types of leadership (fixed, emergent, rotating).
		\end{itemize}
	\item \textit{Predator-Prey Dynamics}
		\begin{itemize}
			\item Implement a predator with different movement pattern.
			\item Give the flock a mechanism to avoid the predator.
			\item How does flocking provide a protection against predation.
		\end{itemize}
	\item \textit{Advanced Perception Model}
		\begin{itemize}
			\item Replace simple radius-based perception with vision cones
			\item Implement occlusion (boids can't see through others)
		\end{itemize}
\end{itemize}


